{\color {red}better title eventually}

### 2015-05-12 cs261n-paper/paper.tex
Abstract editing.

\begin{abstract}
\indent \indent Tor has grown beyond its original purpose and has  since become an important 
Internet circumvention tool. We specifically examine it usability as a censorship circumvention tool, 
an essential facet for adoption and use.  We focus our analysis on the connection configuration dialog of 
Tor browser, as censorship circumvention requires correct transport configurations. 
This study is aimed at evaluating if and how easily users can circumvent censorship using Tor Browser,
isolating specific browser features to study in the process.  To this end, we present the design of
 a large-scale user study examining hundreds of users  on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings. The experiment is scheduled for August 2015.
\end{abstract}

>>>>

\begin{abstract}
\indent \indent Tor has grown beyond its original purpose of anonymity
to become an important tool for
Internet censorship circumvention.
We describe an experiment to assess the usability of Tor Browser,
a web browser with a bundled Tor proxy,
for the purpose of circumvention.
We focus our analysis on the browser's connection configuration dialog,
which enables circumvention even under stringent censors,
when used correctly.
The experiment is aimed at evaluating whether, and how easily users can circumvent censorship using Tor Browser,
under several censorship environments.
We present the design of the experiment,
which will involve hundreds of users completing seven browsing tasks in three different adversarial settings.
We describe the results of a smaller-scale pilot study,
the lessons we learned from it,
and how it guided our future experimental ambitions.
The experiment we describe is scheduled to run in August 2015.
\end{abstract}
